\documentclass[10pt,a4paper]{book}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Aaron Winziers}
\title{Musings}
\begin{document}
	\maketitle
	\chapter{Amsterdam Schiphol - 12-4-2017}
	\section{What am I doing with my life?}
		What the fuck am I doing with my life? It is a question that I find myself asking with increased frequency as of late. Why do I live 9000 km away from home and put myself through the emotional costs of living so far from my mom and dad? Why am I sitting here in Schiphol Airport writing something that sounds like the beginnings of a shitty memoir?
	\section{Because I'm bored.}
		What more reasoning does one need? Because I'm bored can and has been used as an excuse for any manner of things, including whatever the fuck it is I'm writing right now. 
	\section{Fuck my life}
		Only 20 more minutes until boarding now. Tick tock tick tock. Kill me now. I have developed a strong urge to brush my teeth. I feel gross, and now I'm hungry too.
		\\
		I just replaced a period with a question mark in the first paragraph. What am I doing with my life?
	\section{Bored}
		Some moron just burped really loudly. I assume they are American. Crying children irritate me. Why do people bring their kids to airports? I hate kids.
	\section{wat}
		Objectively, I probably look like a psychopath writing all this bullshit out. At least I would if someone were to read what I'm writing.
	\section{I should have gotten drunk}
		On the one hand, I wouldn't hate my life so much right now. On the other hand, however, I'd hate myself so much more than before. Never use intoxicants as a crutch, kids.
	
		
\end{document}