\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{fullpage}
\author{Aaron Winziers}
\title{First read notes}
\begin{document}
	\section*{Introduction, Related work, Preliminaries(Knowledege Bases and Web services)}
\begin{itemize}
	\item \textbf{URI} - an identifier of a real-world entity such as an organisation, a person or an abstract concept. 
	
	\item \textbf{Name} - a human-readable string that identifies the entity. 
	
	\item \textbf{Literal} - a string, a date, or a number. 
	
	\item \textbf{Class} - corresponds to a set of entities, such as the class of singers or the class of cities.
	
	\item \textbf{Relation} - holds between two entities or between an entity and a literal. 
	
	\item \textbf{Fact} - An element of a relation, written r(x, y) to say that the entity with URI x stands in the relation r with the entity with URI y. 
	
	\item \textbf{Knowledge Base(KB)} - a collection of facts. 
	
	\item \textbf{Domain(of a relation)} - the class from which all first arguments of its facts are taken.
	
	\item \textbf{Range} - the class of the second arguments.
	
	\item \textbf{Inverse of a relation r} - written $r^{-}$ , if $\forall x,y: r(x, y) \Leftrightarrow r^{-}(y, x)$
	
	\item \textbf{Functional Relation} - A relation in which no two distinct facts share the relation and the first argument
	
	\item \textbf{Functionality} - $fun(r) := \frac{\#x : \exists y:r(x, y)}{\#x,y:r(x,y)}$
	
	\item $\lambda_{f}(x)$ - root of call result from a given Web Service $f$
	
	\item Edges are labeled by the label of the target node
	
	\item $l_{1}/.../l_{n}(x, y)$ - there is a path along edges $l_{1}...l_{n}$ between $x$ and $y$

\end{itemize}

\section*{Schema Discorvery}
\textbf{\Large It's about discovery, not about data completion}
\subsection*{Probing}
\begin{itemize}
	\item Use entities from KB with the same type as input type from the WS
	\item In WS with multiple input types $t_{1}...t_{n}$:
	\begin{enumerate}
		\item Find "Important" entities of type $t_{1}$ in KB
		\item Find entities of types $t_{2}...t_{n}$ connected to entity for $t_{1}$
		\item Probe WS with entities from step 2
	\end{enumerate}
\end{itemize}
\subsection*{Path Discovery}
\subsection*{Path Alignment}
\subsection*{View \& Transformation Function Construction}
	
	
	
\end{document}